%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{victor}{ sena molero}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Rua Xavier de Almeida, 1135 apt. 192
São Paulo, São Paulo, 04211-001
Brazil
~
+055 (11) 985 511 911
+055 (11) 5062 4849
~
\href{mailto:victorsenam@gmail.com}{victorsenam@gmail.com}
\social{http://github.com/victorsenam}{github}{victorsenam}
\social{http://codeforces.com/profiles/victorsenam}{codeforces}{victorsenam}
\social{https://br.linkedin.com/in/victorsenam}{linkedin}{victorsenam}
\social{http://facebook.com/victoorsena}{facebook}{victoorsena}
\section{languages}
\textbf{portuguese}\hfill native
\textbf{english}\hfill fluent
\section{programming}
C/C++
JavaScript (and Node)
PHP
Ruby (on Rails)
CSS3 \& HTML5
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--current}
{Universidade de São Paulo}
{Bachelor of Computer Science}

\entry
{2011--2013}
{Liceu de Artes e Ofícios de São Paulo}
{Secondary School}

\entry
{2011--2013}
{Liceu de Artes e Ofícios de São Paulo}
{Technical School of Multimedia}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{2013}
{TriForce Soluções Digitais}
{Software Development Internship}
{Took part in the development of web sites for companies and of a generic content managing system which is still in use by the company. Worked mainly with PHP, Javascript and HTML5/CSS3. \\
Some of the websites I've worked on:
\begin{itemize}
\item \href{http://www.gazitbrasil.com.br/}{Gazit Brasil (http://www.gazitbrasil.com.br/)}
\item \href{http://www.mmdermatologia.com.br/}{Clínica Dra. Márcia Monteiro (http://www.mmdermatologia.com.br/)}
\end{itemize}}

\entry
{2012}
{Independent Web-Development}
{Freelancer}
{I worked as a freelancer web developer for about a year with a colleague. It was my first professional experience on which I've build my skills on web development, dealing with clients and teamworking.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{extracurricular}

\begin{entrylist}

%------------------------------------------------

\entry
{2014-current}
{International Collegiate Programming Contest}
{Contestant}
{I'm currently strongly engaged on practicing for the ACM-ICPC competition and other programming contests. Last year my team was the 12\textsuperscript{th} best on the Brazilian Sub-Regional Phase.}

\entry
{2009}
{International Statistical Literacy Competition}
{Finalist}
{I was one of the brazilian representant for my category (from 12 to 14 years old) on the \href{http://iase-web.org/islp/Competitions.php?p=Competitions_2008-2009}{First International Statistical Literacy Competition} held in Durban, South Africa by the International Statistical Institute (ISI) after beeing chosen in a national competition.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

algorithms, competitive programming, web development, statistics, math, discovering interesting stuff, creating useful and cool software, music, gaming.

\end{document}
